---
title: "exercise12"
author: "Lee Rui (BA19008042)"
date: "2020/5/13"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load data 
```{r}
library("raster")
library("rgeos")
library("rgdal")
library("landscapemetrics") 
Sys.getenv("GDAL_DATA")

#remotes::install_github("jannes-m/RQGIS3")
library("RQGIS3")
qgis_session_info()
set_env(dev=FALSE)
#open_app()#Repeat this action will give an error
```

## load point data
```{r}
library("tidyverse")
point_table<-read.csv("E:/RStudio/workspace/ecology/GISBEEBOOK_data/QGIS/points_table.csv")
str(point_table)
point_divided<-point_table %>%separate("ID.POINT_X.POINT_Y", into=c("ID","POINT_X","POINT_Y"),sep=";", convert=TRUE)
point.sp<-SpatialPoints(coords = point_divided[,c("POINT_X","POINT_Y")])
point.spdf<-SpatialPointsDataFrame(point_divided[,c("POINT_X","POINT_Y")],data = point_divided[,2:3])
crs(point.sp)
mycrs<-CRS(projargs="+proj=somerc +lat_0=46.9524055555556 +lon_0=7.43958333333333 +k_0=1 +x_0=600000 +y_0=200000 +ellps=bessel +towgs84=674.374,15.056,405.346,0,0,0,0 +units=m +no_defs",doCheckCRSArgs=TRUE, SRS_string="EPSG:21781")
proj4string(point.spdf)<-mycrs
point.spdf
writeOGR(point.spdf,"E:/RStudio/workspace/ecology/exercise12","point_spdf",driver = "ESRI Shapefile",overwrite = TRUE)
```

## load raster data and reprojection
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r}
g100_06<-raster("E:/RStudio/workspace/ecology/g100_06/g100_06.tif")
find_algorithms(search_term = "Warp")
#get_usage(alg = "gdal:warpreproject")
#get_args_man(alg = "gdal:warpreproject", options = TRUE)
#run_qgis(alg = "gdal:warpreproject", INPUT = g100_06, SOURCE_CRS = "EPSG: 21781", TARGET_CRS= "EPSG: 21781",OUTPUT="E:/RStudio/workspace/ecology/exercise12/g100_06_chcrs.tif")#cost too much time,here load the saved data before
g100_06_chCRS<-raster("E:/RStudio/workspace/ecology/exercise12/g100_06_chcrs.tif")
```

## load vetor data
```{r}
commune_boundary_FR<-readOGR('E:/RStudio/workspace/ecology/GISBEEBOOK_data/QGIS/commune_boundary_FR.shp')
point<-readOGR("E:/RStudio/workspace/ecology/exercise12/point_spdf.shp")
```

# clip and mask
```{r}
projection(g100_06_chCRS)
projection(point)
projection(commune_boundary_FR)
```

```{r}
point_transCRS<-spTransform(point,crs(g100_06_chCRS))
commune_boundary_FR_transCRS<-spTransform(commune_boundary_FR,crs(g100_06_chCRS))

projection(g100_06_chCRS)
projection(commune_boundary_FR_transCRS)
projection(point_transCRS)
```

```{r}
extent(point_transCRS)
extent(g100_06_chCRS)
extent(commune_boundary_FR_transCRS)
```

```{r}
CLC06_Fribourg<-crop(g100_06_chCRS,commune_boundary_FR_transCRS)
CLC06_Fribourg_maskedch<-mask(CLC06_Fribourg,commune_boundary_FR_transCRS,updateNA=TRUE)
writeRaster(CLC06_Fribourg_maskedch,"E:/RStudio/workspace/ecology/exercise12/CLC06_Fribourg_masked.tif",overwrite = TRUE)

```

# add buffer(2000m) and visaulization
```{r}
#raster::extract(CLC06_Fribourg_maskedch,point_transCRS,buffer=2000)
find_algorithms(search_term = "Buffer", name_only = TRUE)
#get_usage(alg = "native:buffer")
#get_args_man(alg = "native:buffer", options = TRUE)
run_qgis(alg = "native:buffer", INPUT = point_transCRS, DISTANCE = 2000, OUTPUT= "E:/RStudio/workspace/ecology/exercise12/buffered.shp")#Repeat this action will give an error
buffer<-readOGR("E:/RStudio/workspace/ecology/exercise12/buffered.shp")
```

```{r}
plot(CLC06_Fribourg_maskedch)
plot(point_transCRS,type = "o", col = "black",add=TRUE)
plot(buffer,type = "o",col = rgb(0, 0, 255, 80, maxColorValue=255),add=TRUE)
```

# calculating proportion and add label
```{r}
POint_buffer<-as(buffer,"SpatialPolygons")
startc=c()
for (i in 1:20){
  POint_bufferm<-mask(CLC06_Fribourg,POint_buffer[i],updateNA=TRUE)
  POint_buffermv<-values(POint_bufferm)
  class12<-sum(POint_buffermv==12,na.rm=TRUE)/(length(POint_buffermv)-sum(is.na(POint_buffermv)))
  class24<-sum(POint_buffermv==24,na.rm=TRUE)/(length(POint_buffermv)-sum(is.na(POint_buffermv)))
  class25<-sum(POint_buffermv==25,na.rm=TRUE)/(length(POint_buffermv)-sum(is.na(POint_buffermv)))
  classother<-1-class12-class24-class25
  startc<-append(startc,c(class12,class24,class25,classother))
}
Land_proportion<-data.frame(t(matrix(c(startc),nrow=4)))
```

```{r}
legend<-read.delim("E:/RStudio/workspace/ecology/g100_06/clc_legend_qgis.txt",skip=1)
str(legend)
clc_legend<-separate(legend,"INTERPOLATION.DISCRETE",into = c("GRID_CODE","b","c","d","e","f"),sep = ",")%>%unite(RGB, c(b, c, d, e), sep = ",", remove = TRUE)%>%separate("f",into = c("CLC_CODE","LABEL"),sep = " - ")
clc_legend
names(Land_proportion)<-c(gsub("-", "_", gsub(" ", "_", clc_legend[which(clc_legend == 12, arr.ind=TRUE)[1],4])),gsub(" ", "_", clc_legend[which(clc_legend == 24, arr.ind=TRUE)[1],4]),gsub(" ", "_", clc_legend[which(clc_legend == 25, arr.ind=TRUE)[1],4]),"Others")
```

```{r}
Landcoor_proportion<-cbind(point_divided,Land_proportion)
Landcoor_proportion#The coordinate deviation of the read-in and read-out data in R leads to a slight deviation in the calculation ratio
```

# visaulization the Land_proportion of points
```{r}
boundary_df<-fortify(commune_boundary_FR_transCRS)
prov_coor<-cbind(boundary_df[which(boundary_df == 15, arr.ind=TRUE)[1:51,1],1:2],commune_boundary_FR_transCRS$GEMNAME)
#prov_coor#Messy coding......
```

```{r}
le<-data.frame(c(589200,589200,589200,589200),c(173000,172000,171000,170000),c("Non-irrigated arable land","Coniferous forest","Mixed forest","Other over land"))#add legend
library("ggplot2")
ggplot()+geom_polygon(aes(x=long, y=lat, group=group), data=boundary_df, fill=cm.colors(2640:2640), colour="grey60")+
  #geom_text(aes(x=long+1000, y=lat,label=paste(commune_boundary_FR_transCRS$GEMNAME)),col=terrain.colors(10)[9],size = 2,check_overlap = TRUE,data=prov_coor)+#rmd doesn't want to show it
  theme(panel.grid = element_blank(), axis.title = element_blank())+
  geom_point(aes(x=POINT_X, y=POINT_Y),alpha=0.2,colour=terrain.colors(10)[7],size = 30,data=point_divided)+
  geom_text(aes(x=POINT_X+800, y=POINT_Y+600, label=paste(ID)), data=point_divided)+
  geom_errorbar(aes(x=POINT_X, ymin=POINT_Y, ymax=POINT_Y+Non_irrigated_arable_land*1000), data=Landcoor_proportion,size=5,color="#ffffa8", width=0)+
  geom_errorbar(aes(x=POINT_X, ymin=POINT_Y+Non_irrigated_arable_land*1000, ymax=POINT_Y+Non_irrigated_arable_land*1000+Coniferous_forest*1000), data=Landcoor_proportion, size=5, color="#00a600", width=0)+
  geom_errorbar(aes(x=POINT_X, ymin=POINT_Y+Non_irrigated_arable_land*1000+Coniferous_forest*1000, ymax=POINT_Y+Non_irrigated_arable_land*1000+Coniferous_forest*1000+Mixed_forest*1000), data=Landcoor_proportion, size=5, color="#4dff00", width=0)+
  geom_errorbar(aes(x=POINT_X, ymin=POINT_Y+Non_irrigated_arable_land*1000+Coniferous_forest*1000+Mixed_forest*1000, ymax=POINT_Y+Non_irrigated_arable_land*1000+Coniferous_forest*1000+Mixed_forest*1000+Others*1000), data=Landcoor_proportion, size=5, color="#ffffff", width=0)+
  ggtitle('Forested land cover percentages surrounding honey bee colonies')+
  geom_text(aes(x=589600, y=175000,label=paste("Legend")),size=4)+
  geom_point(aes(x=le[,1],y=le[,2]),shape=15,colour=c("#ffffa8","#00a600","#4dff00","#ffffff"),size = 4,data=le)+
  geom_text(aes(x=le[,1]+2600, y=le[,2], label=paste(le[,3])), data= le)#(really can't draw the pie)
```

# The following is a model of random guessing
## preProcess data for model
```{r}
Land_proportion$Major_land_types<-apply(Land_proportion, 1, function(x){which.max(x)})
Land_proportion<-Land_proportion%>%mutate(Major_land_types = case_when(Major_land_types == 1 ~ 'Non_irrigated_arable_land',Major_land_types == 2 ~ 'Coniferous_forest',Major_land_types == 3 ~ 'Mixed_forest',Major_land_types == 4 ~ 'Others'))
Land_coor_types<-cbind(point_divided[,2:3],Land_proportion[5])
Land_coor_types
```

## build rf model
```{r}
library("caret")
set.seed(521)
train_idx <- createDataPartition(Land_coor_types$Major_land_types, p=0.75, list=FALSE)
training <- Land_coor_types[train_idx,]
test <- Land_coor_types[-train_idx,]

set.seed(521)
uneLength_ctrl <- trainControl(
  method = 'cv',                  
  number = 10,                     
  savePredictions = 'final',
  classProbs = T,                  
  summaryFunction=twoClassSummary) 

rf_fit <- train(as.factor(Major_land_types) ~.,
                data = training, 
                method = "rf", 
                trControl = uneLength_ctrl,
                verbose = FALSE)

```

## evaluate rf performance
```{r}
rf_pred <- predict(rf_fit, test)
rf_pred
confusionMatrix(reference = as.factor(test$Major_land_types), 
                data = rf_pred,
                mode = "everything")
```

```{r}
library(MLeval)
x <- evalm(rf_fit)
x$roc
x$stdres
```

